High-Throughput Computing on \\ High-Performance Platforms: A Case Study

### 2017-09-10 Experiments.tex
remove comment.

\ifreview
Comments to address in this section:
\begin{enumerate}
    \color{red} 
    \item REVIEWER 3: The scalability benchmarks in section "V.B Experiments"
    should be better explained: what *extacly* is being kept constant in each
    experiment, and what is being varied and over what range. Also the
    captions in the figures do not help much.
\end{enumerate}
\fi

>>>>

% \ifreview
% Comments to address in this section:
% \begin{enumerate}
%     \color{red} 
%     \item REVIEWER 3: The scalability benchmarks in section "V.B Experiments"
%     should be better explained: what *extacly* is being kept constant in each
%     experiment, and what is being varied and over what range. Also the
%     captions in the figures do not help much.
% \end{enumerate}
% \fi
